Concurrent Programming with CXL

### 2020-06-06 book/paper.tex
Starting on new chapter
Added script

@@

@@

>>>>

\begin{figure}
\begin{code}
\begin{verbatim}
cxl -b -c NSLOTS=0 -c NPRODS=1 -c NCONSS=1 PCsema.cxl
cxl -b -c NSLOTS=1 -c NPRODS=0 -c NCONSS=1 PCsema.cxl
cxl    -c NSLOTS=1 -c NPRODS=1 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=1 -c NPRODS=1 -c NCONSS=1 PCsema.cxl
cxl -b -c NSLOTS=1 -c NPRODS=1 -c NCONSS=2 PCsema.cxl
cxl -b -c NSLOTS=1 -c NPRODS=2 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=1 -c NPRODS=2 -c NCONSS=1 PCsema.cxl
cxl    -c NSLOTS=1 -c NPRODS=2 -c NCONSS=2 PCsema.cxl
cxl -b -c NSLOTS=1 -c NPRODS=2 -c NCONSS=3 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=1 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=1 -c NCONSS=1 PCsema.cxl
cxl -b -c NSLOTS=2 -c NPRODS=1 -c NCONSS=2 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=1 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=2 -c NCONSS=2 PCsema.cxl
cxl -b -c NSLOTS=2 -c NPRODS=2 -c NCONSS=3 PCsema.cxl
cxl -b -c NSLOTS=2 -c NPRODS=3 -c NCONSS=0 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=1 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=2 PCsema.cxl
cxl    -c NSLOTS=2 -c NPRODS=3 -c NCONSS=3 PCsema.cxl
\end{verbatim}
\end{code}
\caption{Script for testing producer/consumer synchronization
(assuming the code is in file \texttt{PCsema.cxl}).}
\label{fig:pcscript}
\end{figure}

@@

The first part can be tested with the code given in Figure~\ref{fig:pc}, by
experimenting with different non-negative values for the three constants.
In particular, any run with a positive \texttt{NSLOTS} and
$\mathtt{NCONSS} \le \mathtt{NPRODS} \le \mathtt{NCONSS} + \mathtt{NSLOTS}$
should terminate, while other values should lead to processes blocking.
One could write a script like the one in Figure~\ref{fig:pcscript}.

@@

\chapter{Split Binary Semaphores}
